A parametric system for generating contour parallel toolpaths with adaptive extrusion width

### 2019-08-23 4_method.tex
'bone' ==> 'edge' & 'segment' ==> 'edge' or 'extrusion segment'

\subsubsection{Medial axis transform}
One of the most commonly used skeletonizations of a shape is the medial axis.
The medial axis is defined by the locations where the inscribed circle meets the boundary in at least two locations. \cite{blum1967transformation}
We call the set of closest points on the outline polygon $P$ of a point $v$ on the skeleton its \emph{support}: $\text{sup}(v) = \argmin_{x\in P} |x - v|$.
The resulting skeleton consists of straight segments and parabolic segments which form a graph.
See \cref{MAT_explanation_circles}.
We therefore represent the skeleton in a standard half-edge data-structure.
See \cref{shape_decomposition_datastructure}.

@@

%``Because of its shape, the medial axis of a figure is also called the skeleton or the symmetric axis of the figure.'' \cite{lee1982medial} 
``Associated with the medial axis is a radius function $R$, which defines for each point on the axis its distance to the boundary of the object.'' \cite{lee1982medial}
The medial axis along with the feature radius values along the skeleton combine into a complete shape descriptor, called the medial axis transform (MAT).
Feature radius and node locations of segments will be used below to analyse the shape locally.

@@

\subsubsection{Skeletal trapezoidation}
The MAT decomposes the outline shape into several complex shapes which we need to further decompose in order to have a mesh consisting only of quads and triangles.
We employ a shape decomposition proposed by \citeauthor{Ding2016a}. \cite{Ding2016a}
Each of the regions demarcated by the skeleton is further decomposed by adding radial bones from each node $v$ to its support $\text{sup}(v)$.
The resulting skeleton decomposes the outline shape into trapezoids and triangles.
We will therefore call this shape decomposition the \emph{Skeletal Trapezoidation} (ST).
\footnote{The concept of a trapezoidation conventionally allows for the degenerate case where a trapezoid resolves into a triangle. \cite{chazelle1984,fournier1984}}

@@

The medial axis of a polygonal shape can be obtained from the Voronoi Diagram (VD) generated on the line segments and vertices of the shape, by throwing away all segments of the VD falling outside of the outline shape and throwing away the bones connected to concave vertices in the outline shape. \cite{lee1982medial}
However, the concave vertices are precisely in the support of the nodes to which those bones connect.
This means we can efficiently compute the ST from the VD by removing all segments which lie outside the outline shape and add radial bones to the nodes from there.
See \cref{skeletonization_comparison}.

We then also discretize parabolic segments and segments generated by two concave outline vertices into segments approximately as long as some constant $d^\text{discretization}$.
See \cref{discretization} and the middle of \cref{shape_decomposition_st}.
That way we can approximate the feature radius $R$ in between the two nodes $v_0$ and $v_1$ of a bone in the ST by interpolating linearly between $R(v_0)$ and $R(v_1)$.
This makes the ST capture a discrete approximation of the radius function which is then used to determine the height of each node in the skeleton in order to generate the 3D mesh of the UoC.
%; see \cref{mat_3d}.

@@

We mark a node in the ST as central if its feature radius is larger than that of all of the neighboring nodes.
That is: we mark the local maxima, i.e. the mountain tops of the UoC as being central.
We also mark whole bones as being central if they are significant according to a significance measure which is commonly used in shape analysis.

\subsubsection{Significance measure}\label{sec:significance_measure}
Centrality can be formalized by looking at a commonly used significance measure knows as the \emph{bisector angle}.
The bisector angle $\alpha$ is the interior angle $\angle{p_ovp_1} \leq \si{180}{\degree}$ between a location $v$ on a bone of the ST and its two supporting polygon points $p_0$ and $p_1$.\cite{attali1996modeling}
Bones are significant if the bisector angle exceeds $\alpha_\text{max}$ which is governed by the beading strategy.

For a polygon with a pointy wedge area of an angle $\beta$, we have $\alpha = 180\degree - \beta$, which corresponds to overfill areas and underfill areas the size of $\nicefrac12 w^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$ when filled using a naive strategy of constant bead width $w$.
See \cref{naive_overfill_underfill}.
The bisector angle is therefore an exact measure of the amount of overfill and underfill in the naive toolpaths of constant width.
%Contrary to related literature we will \emph{keep} the non-significant regions of the skeleton.
We mark all significant bones as such and contrary to related literature we keep the unmarked bones of the ST.
Our framework will decide on a beading at all of the marked nodes in `the center' nodes and apply the beading outward to the unmarked nodes.

@@

A computationally efficient way to compute whether an edge is significant can be obtained by looking at the ratio between feature radius $R$ and the Euclidean distance:
if $ | R(v_1) - R(v_0) | / |v_1 - v_0| >  \cos(\alpha_\text{max} / 2)$ then $\alpha > \alpha_\text{max}$.
See \cref{distance_based_angles}.
This means we can prevent executing trigonometric functions on \emph{each} of the bones in the ST.
Moreover the ratio has a clear geometrical interpretation as the slope of the ridge in the UoC surface.

This ratio can readily be applied to simple ST segments to determine whether they are significant.
For segments generated by a polygon vertex at $(0,d)$ and a line segment through $(0,0)$ and $(0,\epsilon)$ or another vertex $(0,0)$, we can determine the significant portion by evaluating $\frac{\partial R}{\partial x} > \cos(\alpha_\text{max} / 2)$.
For parabolas we introduce extra points in the discretization at the two bounds where $| x | = d  / \tan(\alpha_\text{max} / 2)$
and for bones with vertex-vertex support we introduce discretization points at the two bounds where $| x | = \nicefrac12 d  / \tan(\alpha_\text{max} / 2)$.
This ensures that the discretization doesn't alter the extent and existence of marked central regions.
See \cref{legend}.

@@

\subsubsection{Properties of significant regions}
%\begin{lemma} \label{min_euclidean_distance} >> this paragraph contains two lemmas and a concluding remark!
The Euclidean distance between two ST vertices can never be less than the difference in the feature radius $R$ measure between the vertices.
See \cref{distance_ratio_limit}.
The condition $|v - p| = \Delta R$ is true exactly for those sekeletal bones between a node $v$ and an outline location $p$ added by the trapezoidation, which means that the trapezoidation never introduces marked bones, so we can perform the trapezoidation after marking.

@@

\begin{lemma}\label{saddle_points_are_marked}
A saddle point is always marked, i.e.\
when traversing the ST from one locally maximal $R$ to another we must pass through a significant region.
\end{lemma}
\begin{proof}
You will either go through the marked region of a discretized parabola or of a segment with two polygonal vertices as support.
This means that the feature radius function in between marked regions is always monotonic.
This means that when propagating beadings downward from marked regions they can never conflict in the middle - they will always conflict at either marked region.
\end{proof}

\begin{lemma}\label{single_upward_edge}
From any node in the ST which is not a saddle point there is at most a single edge going upward.
\end{lemma}
\begin{proof}
Any branch point $v$ in the MAT coincides with the circumcircle of its support $p_0, p_1, p_2$.
If $v$ lies within $\triangle p_0 p_1 p_2$ it is a local maximum and otherwise we will show it has exactly one upward edge.
If $v$ lies outside of $\triangle p_0 p_1 p_2$ then those support points lie within a \SI{180}{\degree} range from $v$
and one point lies in the middle, say $\angle p_0 + \angle p_1 = \angle p_2$.
Then a circle with radius $R(v) + \epsilon$ around $v'$ such that $|v-v'| < \epsilon$ can only touch $p_0$ and $p_2$.
See \cref{branch_upward_edge_property}.
%See VoronoiQuadrangulation::filterUnmarkedRegions
Bones added because of the trapezoidation always go down to $R=0$, so these don't change the property that each node has at most a single upward edge.
This means that walking up the ST from a marked region to a local maximum follows a single path without branching.
\end{proof}

@@

\subsubsection{Marking filtering}
Using the significance measure and the local maximum feature radius condition we initialize all marked bones and nodes.
We then filter out high frequency changes in the marking in order to ensure that the output of our technique is smooth. 
We perform filtering on the unmarked regions, because unmarking central regions could reintroduce large over- and underfill areas.
From each marked node $v_0$ with an upward unmarked bone attached we walk along the upward edges;
if the total length traversed until we reach another marked node $v_1$ is shorter than some filter distance $d_\text{max}^\text{unmarked}$, we mark all bones encountered as being central.

@@

We first assign each marked node $v$ of the ST the bead count $b^*_v \leftarrow f(2R(v))$.
We then filter out short unmarked regions where the bead count remains constant in order to limit the extent of a problem handled in \cref{section_beading_conflicts}.
From each marked node $v_0$ with an upward unmarked bone attached we walk along the upward edges until we hit another marked node $v_1$.
If the upper node has the same bead count $b^*_{v_1} = b^*_{v_0}$ we mark all bones and nodes $v$ in between, and set the bead count $b^*_v \leftarrow b^*_{v_0}$.

\begin{figure*}
\centering
\setlength{\figwidth}{0.13\textwidth}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__bead_count.pdf}
\caption{Flattened bead counts}\label{beading_transitioning_filtering__bead_count}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transition_mids.pdf}
\caption{Transition anchors}\label{beading_transitioning_filtering__transition_mids}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__filtered.pdf}
\caption{Filtered anchors}\label{beading_transitioning_filtering__filtered}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transition_ends.pdf}
\caption{Transition ramp ends}\label{beading_transitioning_filtering__transition_ends}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transitions_applied.pdf}
\caption{Radial support bones}\label{beading_transitioning_filtering__transitions_applied}
\end{subfigure}
\begin{subfigure}{.27\textwidth}
\hspace*{-.5cm}\includegraphics[width=1.2\columnwidth]{sources/method/beading_transitioning_filtering__result_uoc.png}
\caption{Result UoC}\label{beading_transitioning_filtering__result_uoc}
\end{subfigure}
\caption{
Applying bead counts and transitioning on a shape showing the difference between a simple ST (top) and a mirrored version with small perturbations in the outline (bottom).
Outline in black, medial axis edges in red, radial edges in grey.
\subref{beading_transitioning_filtering__bead_count} First we initialize the bead counts (black) in the marked regions (blue).
\subref{beading_transitioning_filtering__transition_mids} We then extract the anchor locations (purple) of the transitions to a different bead count should be.
\subref{beading_transitioning_filtering__filtered} We then filter out regions of constant bead count.
\subref{beading_transitioning_filtering__transition_ends} We then calculate the end locations (magenta, pink) of the transitions and modify the bead count at nodes in between to fractional values.
\subref{beading_transitioning_filtering__transitions_applied} Finally we introduce nodes at the ends and introduce radial edges (purple) as per the trapezoidation constraint.
The symmetry in the result shows that transitioning is robust against small perturbations in the outline shape.
}
\label{beading_transitioning_filtering}
\end{figure*}

\subsubsection{Flattening}
For bones which connect two nodes $v_0$ and $v_1$ with a different bead count assigned $b^*_{v_0} \neq b^*_{v_1}$ we must figure out the exact location(s $v$ where the flattening operator $f(2R(v))$ jump to a different integer.
We call these locations the \emph{transition anchor positions}.
Rather than applying the jumps to the UoC mesh we calculate the transition anchor positions and apply smoothing based on those positions, so that we modify the UoC mesh afterwards.

We introduce the function $f^{-1}(n) := \argmax_d f(d) = n$, which gives the feature diameter at which $f$ jumps from $n$ to $n+1$ beads.
%For each marked bone between $v_0$ and $v_1$ with $b^*_{v_0} \neq b^*_{v_1}$ we introduce transitions.
A smoothed transition from bead count $n$ to $n+1$ will be anchored on each location $v_x$ where $R(v_x) = f^{-1}(n)$.
We can compute the location of the anchor simply as
$$v_x = v_0 + (v_1 - v_0) \frac{ f^{-1}(n) - R(v_0) }{ R(v_1) - R(v_0) }$$
for each $n$ such that $b^*_{v_0}<n<b^*_{v_1}$.
See \cref{beading_transitioning_filtering__transition_mids}.

@@

A transition with length $t(n)$ will be placed somewhere covering the transition anchor position.
We require an additional function to be specified by the beading strategy: $t_0(n)$ determines the distance between the lower end of a transition from bead count $n$ to $n+1$ and the anchor point - as measured along the marked bones of the ST.
From that we calculate $t_1(n) = t(n) - t_0(n)$ for the distance from the anchor to the upper end of the transition.
For our example we can simply use $t_0(n) = t_1(n) = \nicefrac12 w_\text{pref}$, so that the transition ramp is centered on the anchor position.

@@

The generation of the transition ramps should be robust against small perturbations in the outline shape;
compare the top and bottom of \cref{beading_transitioning_filtering}.
In order to generate the lower and upper end point of the transition ramps we walk downward and upward along the marked regions from each anchor position $v$ until we have traversed the corresponding distance of $t_{0}(n)$ or $t_{1}(n)$.
If there is any node $v_x$ in between $v$ and $v_0$ or $v_1$ we assign it a fractional bead count by linear interpolation: $b^*_{v_x} = n + D(v_0, v_x)/t(n)$, where $D(.)$ is the cumulative distance measured along the marked bone(s).
See \cref{beading_transitioning_filtering__transition_ends}.
These fractional bead counts will be used in \cref{section_beading_interpolation} in a way which guarantees a similar toolpath in transitioning regions which are crossed by extra support bones for small perturbations and those which are not.

Finally we perform the mesh update by introducing nodes at the transition ends and introducing radial support bones from these new nodes to the outline as per the trapezoidation requirement.
We end up with a UoC with marked regions altered to be horizontal at integer multiples of half the nozzle width for long stretches with ramps in between.
See \cref{beading_transitioning_filtering__transitions_applied} and \subref{beading_transitioning_filtering__result_uoc}.

@@

For the purpose of generating toolpaths we only need to define the height at the locations which will be part of a slice, rather than at all locations in the periphery.
Instead of adjusting the height of peripheral mesh nodes, we determine the locations along the bones where the adjusted height coincides with a slicing height.
In this section we will show how we can define a mapping from radial distance values to the indices of slicing heights, called a \emph{beading},
how each beading is calculated for a central node
and how the beadings are propagated outward to peripheral nodes.
This helps to define an efficient slicing algorithm in \cref{sec_toolpath_extraction}.

@@

\subsubsection{Beading interpolation}\label{section_beading_interpolation}
Central nodes which are in the middle of a transition have obtained a fractional bead count, but the definition of a beading presupposed integer numbers.
In order to generate a beading for a central node with a fractional bead count assigned we use the fractional part of the bead count to interpolate between two beadings defined on the fractional bead count rounded up and down.
Suppose we want to interpolate between two beadings $B^V$ and $B^W$, for which $n^{B^V} < n^{B^W}$.
We interpolate the diameter $d$, widths $w_i$ and locations $l_i$ for indices $i < \nicefrac12 n^{B^V}$ linearly and enforce the symmetry constraints on the upper indices.
See \cref{beading_interpolation}.
The linear interpolation enforces robustness against small perturbations in the outline shape which cause extra bones to appear in the ST inside of transition regions.

@@

\subsubsection{Beading propagation}\label{section_beading_conflicts}
The beading information associated with the central nodes is then propagated outward throughout the whole mesh.
However, beading conflicts can arise where a marked bone has unmarked upward edges attached to them, since beading will also be propagated down from the local maxima or other higher marked regions.
See \cref{beading_conflict_problem}.
In such a case we interpolate between the lower beading and the beading propagated from above,
starting from the lower marked node and ending at a distance $t_\text{beading}$ upward.
At the nodes in between we will apply the interpolation between the two beadings and propagate the interpolated beading outward from those nodes.
This interpolation is performed during the beading propagation algorithm.

@@

\subsection{Toolpath extraction}\label{sec_toolpath_extraction}
Now that each node has a beading associated with it we can apply the beading to generate the junctions of the toolpaths.
For each upward half-edge $e$ we generate each junction $J$ based on the beading $B = B^{v_1^e}$:
\begin{align*}
J &= \{ v, w, i \} \\ 
v &= v_1^e + (v_0^e - v_1^e) \frac{R(v_1^e) - l_i^B}{R(v_1^e) - R(v_0^e)} \\ 
w &= w_i^B
% \\ i^J &= i
\end{align*}
for any $i$ for which $R(v_0^e) < l_i^B \leq R(v_1^e)$.
See \cref{junction_placement}.
We store all junctions of a segment in a mapping from edge to a list of junctions.

>>>>

\subsubsection{Medial axis transform}
One of the most commonly used skeletonizations of a shape is the medial axis.
The medial axis is defined by the locations where the inscribed circle meets the boundary in at least two locations. \cite{blum1967transformation}
We call the set of closest points on the outline polygon $P$ of a point $v$ on the skeleton its \emph{support}: $\text{sup}(v) = \argmin_{x\in P} |x - v|$.
The resulting skeleton consists of straight edges and parabolic edges which form a graph.
See \cref{MAT_explanation_circles}.
We therefore represent the skeleton in a standard half-edge data-structure.
See \cref{shape_decomposition_datastructure}.

@@

%``Because of its shape, the medial axis of a figure is also called the skeleton or the symmetric axis of the figure.'' \cite{lee1982medial} 
``Associated with the medial axis is a radius function $R$, which defines for each point on the axis its distance to the boundary of the object.'' \cite{lee1982medial}
The medial axis along with the feature radius values along the skeleton combine into a complete shape descriptor, called the medial axis transform (MAT).
Feature radius and node locations will be used below to analyse the shape locally.

@@

\subsubsection{Skeletal trapezoidation}
The MAT decomposes the outline shape into several complex shapes which we need to further decompose in order to have a mesh consisting only of quads and triangles.
We employ a shape decomposition proposed by \citeauthor{Ding2016a}. \cite{Ding2016a}
Each of the regions demarcated by the skeleton is further decomposed by adding radial edges from each node $v$ to its support $\text{sup}(v)$.
The resulting skeleton decomposes the outline shape into trapezoids and triangles.
We will therefore call this shape decomposition the \emph{Skeletal Trapezoidation} (ST).
\footnote{The concept of a trapezoidation conventionally allows for the degenerate case where a trapezoid resolves into a triangle. \cite{chazelle1984,fournier1984}}

@@

The medial axis of a polygonal shape can be obtained from the Voronoi Diagram (VD) generated on the line segments and vertices of the shape, by throwing away all edges of the VD falling outside of the outline shape and throwing away the edges connected to concave vertices in the outline shape. \cite{lee1982medial}
However, the concave vertices are precisely in the support of the nodes to which those edges connect.
This means we can efficiently compute the ST from the VD by removing all edges which lie outside the outline shape and add radial edges to the nodes from there.
See \cref{skeletonization_comparison}.

We then also discretize parabolic edges and edges generated by two concave outline vertices into edges approximately as long as some constant $d^\text{discretization}$.
See \cref{discretization} and the middle of \cref{shape_decomposition_st}.
That way we can approximate the feature radius $R$ in between the two nodes $v_0$ and $v_1$ of an edge in the ST by interpolating linearly between $R(v_0)$ and $R(v_1)$.
This makes the ST capture a discrete approximation of the radius function which is then used to determine the height of each node in the skeleton in order to generate the 3D mesh of the UoC.
%; see \cref{mat_3d}.

@@

We mark a node in the ST as central if its feature radius is larger than that of all of the neighboring nodes.
That is: we mark the local maxima, i.e. the mountain tops of the UoC as being central.
We also mark whole edges as being central if they are significant according to a significance measure which is commonly used in shape analysis.

\subsubsection{Significance measure}\label{sec:significance_measure}
Centrality can be formalized by looking at a commonly used significance measure knows as the \emph{bisector angle}.
The bisector angle $\alpha$ is the interior angle $\angle{p_ovp_1} \leq \si{180}{\degree}$ between a location $v$ on an edge of the ST and its two supporting polygon points $p_0$ and $p_1$.\cite{attali1996modeling}
Edges are significant if the bisector angle exceeds $\alpha_\text{max}$ which is governed by the beading strategy.

For a polygon with a pointy wedge area of an angle $\beta$, we have $\alpha = 180\degree - \beta$, which corresponds to overfill areas and underfill areas the size of $\nicefrac12 w^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$ when filled using a naive strategy of constant bead width $w$.
See \cref{naive_overfill_underfill}.
The bisector angle is therefore an exact measure of the amount of overfill and underfill in the naive toolpaths of constant width.
%Contrary to related literature we will \emph{keep} the non-significant regions of the skeleton.
We mark all significant edges as such and contrary to related literature we keep the unmarked edges of the ST.
Our framework will decide on a beading at all of the marked nodes in `the center' nodes and apply the beading outward to the unmarked nodes.

@@

A computationally efficient way to compute whether an edge is significant can be obtained by looking at the ratio between feature radius $R$ and the Euclidean distance:
if $ | R(v_1) - R(v_0) | / |v_1 - v_0| >  \cos(\alpha_\text{max} / 2)$ then $\alpha > \alpha_\text{max}$.
See \cref{distance_based_angles}.
This means we can prevent executing trigonometric functions on \emph{each} of the edges in the ST.
Moreover the ratio has a clear geometrical interpretation as the slope of the ridge in the UoC surface.

This ratio can readily be applied to simple ST edges to determine whether they are significant.
For VD edges generated by a polygon vertex at $(0,d)$ and a line segment through $(0,0)$ and $(0,\epsilon)$ or another vertex $(0,0)$, we can determine the significant portion by evaluating $\frac{\partial R}{\partial x} > \cos(\alpha_\text{max} / 2)$.
For parabolas we introduce extra points in the discretization at the two bounds where $| x | = d  / \tan(\alpha_\text{max} / 2)$
and for VD edges with vertex-vertex support we introduce discretization points at the two bounds where $| x | = \nicefrac12 d  / \tan(\alpha_\text{max} / 2)$.
This ensures that the discretization we perform when transforming the VD into the ST doesn't alter the extent and existence of marked central regions.
See \cref{legend}.

@@

\subsubsection{Properties of significant regions}
%\begin{lemma} \label{min_euclidean_distance} >> this paragraph contains two lemmas and a concluding remark!
The Euclidean distance between two ST vertices can never be less than the difference in the feature radius $R$ measure between the vertices.
See \cref{distance_ratio_limit}.
The condition $|v - p| = \Delta R$ is true exactly for those ST edges between a node $v$ and an outline location $p$ added by the trapezoidation, which means that the trapezoidation never introduces marked edges, so we can perform the trapezoidation after marking.

@@

\begin{lemma}\label{saddle_points_are_marked}
A saddle point is always marked, i.e.\
when traversing the ST from one locally maximal $R$ to another we must pass through a significant region.
\end{lemma}
\begin{proof}
You will either go through the marked region of a discretized parabola or of an edge with two polygonal vertices as support.
This means that the feature radius function in between marked regions is always monotonic.
This means that when propagating beadings downward from marked regions they can never conflict in the middle - they will always conflict at either marked region.
\end{proof}

\begin{lemma}\label{single_upward_edge}
From any node in the ST which is not a saddle point there is at most a single edge going upward.
\end{lemma}
\begin{proof}
Any branch point $v$ in the MAT coincides with the circumcircle of its support $p_0, p_1, p_2$.
If $v$ lies within $\triangle p_0 p_1 p_2$ it is a local maximum and otherwise we will show it has exactly one upward edge.
If $v$ lies outside of $\triangle p_0 p_1 p_2$ then those support points lie within a \SI{180}{\degree} range from $v$
and one point lies in the middle, say $\angle p_0 + \angle p_1 = \angle p_2$.
Then a circle with radius $R(v) + \epsilon$ around $v'$ such that $|v-v'| < \epsilon$ can only touch $p_0$ and $p_2$.
See \cref{branch_upward_edge_property}.
%See VoronoiQuadrangulation::filterUnmarkedRegions
Edges added because of the trapezoidation always go down to $R=0$, so these don't change the property that each node has at most a single upward edge.
This means that walking up the ST from a marked region to a local maximum follows a single path without branching.
\end{proof}

@@

\subsubsection{Marking filtering}
Using the significance measure and the local maximum feature radius condition we initialize all marked edges and nodes.
We then filter out high frequency changes in the marking in order to ensure that the output of our technique is smooth. 
We perform filtering on the unmarked regions, because unmarking central regions could reintroduce large over- and underfill areas.
From each marked node $v_0$ with an upward unmarked edge attached we walk along the upward edges;
if the total length traversed until we reach another marked node $v_1$ is shorter than some filter distance $d_\text{max}^\text{unmarked}$, we mark all edges encountered as being central.

@@

We first assign each marked node $v$ of the ST the bead count $b^*_v \leftarrow f(2R(v))$.
We then filter out short unmarked regions where the bead count remains constant in order to limit the extent of a problem handled in \cref{section_beading_conflicts}.
From each marked node $v_0$ with an upward unmarked edge attached we walk along the upward edges until we hit another marked node $v_1$.
If the upper node has the same bead count $b^*_{v_1} = b^*_{v_0}$ we mark all edges and nodes $v$ in between, and set the bead count $b^*_v \leftarrow b^*_{v_0}$.

\begin{figure*}
\centering
\setlength{\figwidth}{0.13\textwidth}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__bead_count.pdf}
\caption{Flattened bead counts}\label{beading_transitioning_filtering__bead_count}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transition_mids.pdf}
\caption{Transition anchors}\label{beading_transitioning_filtering__transition_mids}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__filtered.pdf}
\caption{Filtered anchors}\label{beading_transitioning_filtering__filtered}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transition_ends.pdf}
\caption{Transition ramp ends}\label{beading_transitioning_filtering__transition_ends}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transitions_applied.pdf}
\caption{Radial support edges}\label{beading_transitioning_filtering__transitions_applied}
\end{subfigure}
\begin{subfigure}{.27\textwidth}
\hspace*{-.5cm}\includegraphics[width=1.2\columnwidth]{sources/method/beading_transitioning_filtering__result_uoc.png}
\caption{Result UoC}\label{beading_transitioning_filtering__result_uoc}
\end{subfigure}
\caption{
Applying bead counts and transitioning on a shape showing the difference between a simple ST (top) and a mirrored version with small perturbations in the outline (bottom).
Outline in black, medial axis edges in red, radial edges in grey.
\subref{beading_transitioning_filtering__bead_count} First we initialize the bead counts (black) in the marked regions (blue).
\subref{beading_transitioning_filtering__transition_mids} We then extract the anchor locations (purple) of the transitions to a different bead count should be.
\subref{beading_transitioning_filtering__filtered} We then filter out regions of constant bead count.
\subref{beading_transitioning_filtering__transition_ends} We then calculate the end locations (magenta, pink) of the transitions and modify the bead count at nodes in between to fractional values.
\subref{beading_transitioning_filtering__transitions_applied} Finally we introduce nodes at the ends and introduce radial edges (purple) as per the trapezoidation constraint.
The symmetry in the result shows that transitioning is robust against small perturbations in the outline shape.
}
\label{beading_transitioning_filtering}
\end{figure*}

\subsubsection{Flattening}
For edges which connect two nodes $v_0$ and $v_1$ with a different bead count assigned $b^*_{v_0} \neq b^*_{v_1}$ we must figure out the exact location(s $v$ where the flattening operator $f(2R(v))$ jump to a different integer.
We call these locations the \emph{transition anchor positions}.
Rather than applying the jumps to the UoC mesh we calculate the transition anchor positions and apply smoothing based on those positions, so that we modify the UoC mesh afterwards.

We introduce the function $f^{-1}(n) := \argmax_d f(d) = n$, which gives the feature diameter at which $f$ jumps from $n$ to $n+1$ beads.
%For each marked edge between $v_0$ and $v_1$ with $b^*_{v_0} \neq b^*_{v_1}$ we introduce transitions.
A smoothed transition from bead count $n$ to $n+1$ will be anchored on each location $v_x$ where $R(v_x) = f^{-1}(n)$.
We can compute the location of the anchor simply as
$$v_x = v_0 + (v_1 - v_0) \frac{ f^{-1}(n) - R(v_0) }{ R(v_1) - R(v_0) }$$
for each $n$ such that $b^*_{v_0}<n<b^*_{v_1}$.
See \cref{beading_transitioning_filtering__transition_mids}.

@@

A transition with length $t(n)$ will be placed somewhere covering the transition anchor position.
We require an additional function to be specified by the beading strategy: $t_0(n)$ determines the distance between the lower end of a transition from bead count $n$ to $n+1$ and the anchor point - as measured along the marked edges of the ST.
From that we calculate $t_1(n) = t(n) - t_0(n)$ for the distance from the anchor to the upper end of the transition.
For our example we can simply use $t_0(n) = t_1(n) = \nicefrac12 w_\text{pref}$, so that the transition ramp is centered on the anchor position.

@@

The generation of the transition ramps should be robust against small perturbations in the outline shape;
compare the top and bottom of \cref{beading_transitioning_filtering}.
In order to generate the lower and upper end point of the transition ramps we walk downward and upward along the marked regions from each anchor position $v$ until we have traversed the corresponding distance of $t_{0}(n)$ or $t_{1}(n)$.
If there is any node $v_x$ in between $v$ and $v_0$ or $v_1$ we assign it a fractional bead count by linear interpolation: $b^*_{v_x} = n + D(v_0, v_x)/t(n)$, where $D(.)$ is the cumulative distance measured along the marked edge(s).
See \cref{beading_transitioning_filtering__transition_ends}.
These fractional bead counts will be used in \cref{section_beading_interpolation} in a way which guarantees a similar toolpath in transitioning regions which are crossed by extra support edges for small perturbations and those which are not.

Finally we perform the mesh update by introducing nodes at the transition ends and introducing radial support edges from these new nodes to the outline as per the trapezoidation requirement.
We end up with a UoC with marked regions altered to be horizontal at integer multiples of half the nozzle width for long stretches with ramps in between.
See \cref{beading_transitioning_filtering__transitions_applied} and \subref{beading_transitioning_filtering__result_uoc}.

@@

For the purpose of generating toolpaths we only need to define the height at the locations which will be part of a slice, rather than at all locations in the periphery.
Instead of adjusting the height of peripheral mesh nodes, we determine the locations along the edges where the adjusted height coincides with a slicing height.
In this section we will show how we can define a mapping from radial distance values to the indices of slicing heights, called a \emph{beading},
how each beading is calculated for a central node
and how the beadings are propagated outward to peripheral nodes.
This helps to define an efficient slicing algorithm in \cref{sec_toolpath_extraction}.

@@

\subsubsection{Beading interpolation}\label{section_beading_interpolation}
Central nodes which are in the middle of a transition have obtained a fractional bead count, but the definition of a beading presupposed integer numbers.
In order to generate a beading for a central node with a fractional bead count assigned we use the fractional part of the bead count to interpolate between two beadings defined on the fractional bead count rounded up and down.
Suppose we want to interpolate between two beadings $B^V$ and $B^W$, for which $n^{B^V} < n^{B^W}$.
We interpolate the diameter $d$, widths $w_i$ and locations $l_i$ for indices $i < \nicefrac12 n^{B^V}$ linearly and enforce the symmetry constraints on the upper indices.
See \cref{beading_interpolation}.
The linear interpolation enforces robustness against small perturbations in the outline shape which cause extra edges to appear in the ST inside of transition regions.

@@

\subsubsection{Beading propagation}\label{section_beading_conflicts}
The beading information associated with the central nodes is then propagated outward throughout the whole mesh.
However, beading conflicts can arise where a marked edge has unmarked upward edges attached to them, since beading will also be propagated down from the local maxima or other higher marked regions.
See \cref{beading_conflict_problem}.
In such a case we interpolate between the lower beading and the beading propagated from above,
starting from the lower marked node and ending at a distance $t_\text{beading}$ upward.
At the nodes in between we will apply the interpolation between the two beadings and propagate the interpolated beading outward from those nodes.
This interpolation is performed during the beading propagation algorithm.

@@

\subsection{Toolpath extraction}\label{sec_toolpath_extraction}
Now that each node has a beading associated with it we can apply the beading to generate the junctions of the toolpaths.
For each upward half-edge $e$ we generate each junction $J$ based on the beading $B = B^{v_1^e}$:
\begin{align*}
J &= \{ v, w, i \} \\ 
v &= v_1^e + (v_0^e - v_1^e) \frac{R(v_1^e) - l_i^B}{R(v_1^e) - R(v_0^e)} \\ 
w &= w_i^B
% \\ i^J &= i
\end{align*}
for any $i$ for which $R(v_0^e) < l_i^B \leq R(v_1^e)$.
See \cref{junction_placement}.
We store all junctions of an edge in a mapping from edge to a list of junctions.

\begin{figure}
\centering
\setlength{\figheight}{.29\columnwidth}
\begin{subfigure}{0.14\columnwidth}\centering
\includegraphics[height=\figheight]{sources/method/trapezoid_beading_beading.pdf}
\caption{Beadings}\label{trapezoid_beading_beading}
\end{subfigure}
\begin{subfigure}{0.5\columnwidth}\centering
\includegraphics[height=\figheight]{sources/method/trapezoid_beading_propagated.pdf}
\caption{Single beading propagated to all nodes}\label{trapezoid_beading_propagated}
\end{subfigure}
\begin{subfigure}{0.34\columnwidth}\centering
\includegraphics[height=\figheight]{sources/method/trapezoid_beading_separate.pdf}
\caption{Separate beadings at either top node}\label{trapezoid_beading_separate}
\end{subfigure}
\caption{
Applying beadings togenerate junctions along trapezoids.
\subref{trapezoid_beading_beading} shows half of the locations $l_i$ and widths $w_i$ of two arbitrary different beadings.
\subref{trapezoid_beading_propagated} shows the application of $B^1$ to the various types of trapezoid.
\subref{trapezoid_beading_separate} shows how a trapezoid with a marked edge will have two different beadings assigned, which will generate their respective junctions along the support edges.
No junctions will be generated along marked edges.
Wide black lines are outline segments, marked nodes and edges in blue, the junctions in yellow and green wavefronts of equidistant radial distance at $R = l_i$.
}
\label{junction_placement}
\end{figure}

We then generate extrusion segments for each trapezoid by connecting together the junctions of the same index.
See \cref{segment_generation}.
If the amount of junctions on both sides of the trapezoid is not the same then this trapezoid is in a transition and we leave one inner junction unconnected.
If a central edge has both nodes with an odd bead count assigned to it $b^* \bmod 2 = 1 $ we should prevent the algorithm from generating the center extrusion segment from both trapezoids.
We therefore use some arbitrary condition to decide which one of the two to include based on the ordering of the coordinates of $v_0$ and $v_1$.
